---
title: "Report"
output:
  word_document: default
  pdf_document: default
---
# Read data
```{r}
encounter <- read.csv("/Users/liyi/Desktop/RP/day_in_the_life.csv")
```
# How many unique subjects in this data set
```{r}
index <- duplicated(encounter[,1])
encounter_subset <- encounter[!index,]
(nrow(encounter_subset))
```
# Change age to age range
```{r}
age_range_rep <- encounter_subset$Age
i = 1
while(i<=length(age_range_rep)){
  age = age_range_rep[i]
  if(age>=0&&age<10)
  {
    age_range_rep[i] = "0-10"
  }
  else if(age>=10&&age<20){
    age_range_rep[i] = "10-20"
  }
  else if(age>=20&&age<30)
  {
    age_range_rep[i] = "20-30"
  }
  else if(age>=30&&age<40)
  {
    age_range_rep[i] = "30-40"
  }
  else if(age>=40&&age<50)
  {
    age_range_rep[i] = "40-50"
  }
  else if(age>=50&&age<60)
  {
    age_range_rep[i] = "50-60"
  }
  else if(age>=60&&age<70)
  {
    age_range_rep[i] = "60-70"
  }
  else if(age>=70&&age<80)
  {
    age_range_rep[i] = "70-80"
  }
  else if(age>=80&&age<90)
  {
    age_range_rep[i] = "80-90"
  }
  else if(age>=90&&age<100)
  {
    age_range_rep[i] = "90-100"
  }
  else
  {
    age_range_rep[i] = "no age"
  }
  i = i+1
}
```

# Relationship between age and num of locations
##  Make plot of age and num of locations
```{r}
num_of_locations <- data.frame(num = numeric(0))
for(subject in encounter_subset$Subject){
  #print(subject)
  num_of_locations <- rbind(num_of_locations, nrow(encounter[which(encounter$Subject == subject), ]))
  #nrow(encounter[which(encounter$Subject == subject), ])
}
num_of_locations$age <- encounter_subset$Age
nrow(num_of_locations)
plot(num_of_locations$X1L~num_of_locations$age,xlab = "Age",ylab = "Number of locations")
```
##  There is no obvious relationship between age and the number of locations, so I rewrite age to age range.
##  Rewrite number larger than 12 to "more than 12"
```{r}
num_of_locations$location_range <- num_of_locations$X1L
num_of_locations$location_range[num_of_locations$location_range > 12] <- 13
num_of_locations$location_range <- factor(num_of_locations$location_range,
                                          levels = c(1,2,3,4,5,6,7,8,9,10,11,12,13),
                                          labels = c("1","2","3","4","5","6","7","8","9","10","11","12",">12"))
num_of_locations$age_range <- age_range_rep
```
##  Make barplot for age range and the number of locations. It is convenient for us to analyze the distribution of different numbers in one range, and the distribution of age range of a number.
##  Make barplot
```{r}
agelocation <- table(num_of_locations$location_range,num_of_locations$age_range)
lacationage <- table(num_of_locations$age_range,num_of_locations$location_range)
par(mar=c(5.1, 4.1, 4.1, 8.1), xpd=TRUE)
barplot(agelocation, main="Age range and locations",
        xlab="Age range", ylab = "Frequency",
        col=c("darkblue","red","orange","yellow","green","blue","purple","darkslategray3","gray","black","pink","darkred","cornsilk"),
        beside=TRUE)
text.legend=row.names(agelocation)
col2 <- c("darkblue","red","orange","yellow","green","blue","purple","darkslategray3","gray","black","pink","darkred","cornsilk")
legend("topright",pch=c(15,15,16,16),legend=text.legend,col=col2,bty="n",ncol = 1,,inset=c(-0.25,0))

barplot(agelocation, main="Age range and locations",
        xlab="Age range", ylab = "Frequency",
        col=c("darkblue","red","orange","yellow","green","blue","purple","darkslategray3","gray","black","pink","darkred","cornsilk")
        )
text.legend=row.names(agelocation)
col2 <- c("darkblue","red","orange","yellow","green","blue","purple","darkslategray3","gray","black","pink","darkred","cornsilk")
legend("topright",pch=c(15),legend=text.legend,col=col2,bty="n",ncol = 1,inset=c(-0.25,0))

barplot(lacationage, main="Age range and locations",
        xlab="Number of locations", ylab = "Frequency",
        col=c("darkblue","red","orange","yellow","green","blue","purple","darkslategray3","gray"),
        beside=TRUE)
text.legend=row.names(lacationage)
col2 <- c("darkblue","red","orange","yellow","green","blue","purple","darkslategray3","gray")
legend("topright",pch=c(15),legend=text.legend,col=col2,bty="n",ncol = 1,inset=c(-0.25,0))

barplot(lacationage, main="Age range and locations",
        xlab="Number of locations", ylab = "Frequency",
        col=c("darkblue","red","orange","yellow","green","blue","purple","darkslategray3","gray")
        )
text.legend=row.names(lacationage)
col2 <- c("darkblue","red","orange","yellow","green","blue","purple","darkslategray3","gray")
legend("topright",pch=c(15),legend=text.legend,col=col2,bty="n",ncol = 1,inset=c(-0.25,0))

```
##  Make barplot for distribution of probabilities
```{r}
agelocation_prop1 <- prop.table(agelocation,2)
barplot(agelocation_prop1, main="Probabilities age range and locations",
        xlab="Age range", ylab = "Probabilities",
        col=c("darkblue","red","orange","yellow","green","blue","purple","darkslategray3","gray","black","pink","darkred","cornsilk"))
text.legend=row.names(agelocation_prop1)
col2 <- c("darkblue","red","orange","yellow","green","blue","purple","darkslategray3","gray","black","pink","darkred","cornsilk")
legend("topright",pch=c(15),legend=text.legend,col=col2,bty="n",ncol = 1,inset=c(-0.25,0))

lacationage_prop1 <- prop.table(lacationage,2)
barplot(lacationage_prop1, main="Probabilities age range and locations",
        xlab="Locations", ylab = "Probabilities",
        col=c("darkblue","red","orange","yellow","green","blue","purple","darkslategray3","gray","black","pink","darkred","cornsilk"))
text.legend=row.names(lacationage_prop1)
col2 <- c("darkblue","red","orange","yellow","green","blue","purple","darkslategray3","gray","black","pink","darkred","cornsilk")
legend("topright",pch=c(15),legend=text.legend,col=col2,bty="n",ncol = 1,inset=c(-0.25,0))

```
# Relationship between age and num of location types
##  Plot
```{r}
index <- duplicated(encounter[,c(1,6)])
encounter_subset_locationType <- encounter[!index,]
num_of_locationTypes <- data.frame(num = numeric(0))
for(subject in encounter_subset$Subject){
  num_of_locationTypes <- rbind(num_of_locationTypes, nrow(encounter_subset_locationType[which(encounter_subset_locationType$Subject == subject), ]))
}
num_of_locationTypes$age <- encounter_subset$Age
plot(num_of_locationTypes$X1L~num_of_locationTypes$age,xlab = "Age",ylab = "Number of location types")
```
##  Make barplot
```{r}
num_of_locationTypes$age_range <- age_range_rep
agetype <- table(num_of_locationTypes$X1L,num_of_locationTypes$age_range)
typeage <- table(num_of_locationTypes$age_range,num_of_locationTypes$X1L)
barplot(agetype, main="Age range and location types",
        xlab="Age range", ylab = "Frequency",
        col=c("darkblue","red","orange","yellow","green","blue","purple","darkslategray3","gray"),
        beside=TRUE)
text.legend=row.names(agetype)
col2 <- c("darkblue","red","orange","yellow","green","blue","purple","darkslategray3","gray")
legend("topright",pch=c(15),legend=text.legend,col=col2,bty="n",ncol = 1,inset=c(-0.25,0))

barplot(agetype, main="Age range and location types",
        xlab="Age range", ylab = "Frequency",
        col=c("darkblue","red","orange","yellow","green","blue","purple","darkslategray3","gray"))
text.legend=row.names(agetype)
col2 <- c("darkblue","red","orange","yellow","green","blue","purple","darkslategray3","gray")
legend("topright",pch=c(15),legend=text.legend,col=col2,bty="n",ncol = 1,inset=c(-0.25,0))

barplot(typeage, main="Age range and location types",
        xlab="Number of location types", ylab = "Frequency",
        col=c("darkblue","red","orange","yellow","green","blue","purple","darkslategray3","gray"),
        beside=TRUE)
text.legend=row.names(typeage)
col2 <- c("darkblue","red","orange","yellow","green","blue","purple","darkslategray3","gray")
legend("topright",pch=c(15),legend=text.legend,col=col2,bty="n",ncol = 1,inset=c(-0.25,0))

barplot(typeage, main="Age range and location types",
        xlab="Number of location types", ylab = "Frequency",
        col=c("darkblue","red","orange","yellow","green","blue","purple","darkslategray3","gray"))
text.legend=row.names(typeage)
col2 <- c("darkblue","red","orange","yellow","green","blue","purple","darkslategray3","gray")
legend("topright",pch=c(15),legend=text.legend,col=col2,bty="n",ncol = 1,inset=c(-0.25,0))

```
##  Make barplot for distribution of probabilities
```{r}
agetype_prop1 <- prop.table(agetype,2)
barplot(agetype_prop1, main="Probabilities age range and location types",
        xlab="Age range", ylab = "Probabilities",
        col=c("darkblue","red","orange","yellow","green","blue","purple","darkslategray3","gray"))
text.legend=row.names(agetype_prop1)
col2 <- c("darkblue","red","orange","yellow","green","blue","purple","darkslategray3","gray")
legend("topright",pch=c(15),legend=text.legend,col=col2,bty="n",ncol = 1,inset=c(-0.25,0))

typeage_prop <- prop.table(typeage,2)
barplot(typeage_prop, main="Probabilities age range and locations",
        xlab="Locations", ylab = "Probabilities",
        col=c("darkblue","red","orange","yellow","green","blue","purple","darkslategray3","gray","black","pink","darkred","cornsilk"))
text.legend=row.names(typeage_prop)
col2 <- c("darkblue","red","orange","yellow","green","blue","purple","darkslategray3","gray","black","pink","darkred","cornsilk")
legend("topright",pch=c(15),legend=text.legend,col=col2,bty="n",ncol = 1,inset=c(-0.25,0))

```
# Relationship between gender and number of locations
```{r}
num_of_locations$gender <- encounter_subset$Gender
num_of_locations$gender <- factor(num_of_locations$gender,
                                  levels = c(1,2),
                                  labels = c("Male","Female"))
genderlocation <- table(num_of_locations$gender,num_of_locations$location_range)
locationgender <- table(num_of_locations$location_range,num_of_locations$gender)
barplot(genderlocation,main = "Gender and num of locations", 
        xlab = "Locations", ylab = "Frequency",
        col = c("darkblue","red"),
        beside = TRUE)
text.legend=row.names(genderlocation)
col2 <- c("darkblue","red")
legend("topright",pch=c(15),legend=text.legend,col=col2,bty="n",ncol = 1,inset=c(-0.25,0))

barplot(locationgender,main = "Gender and num of locations", 
        xlab = "Locations", ylab = "Frequency",
        col=c("darkblue","red","orange","yellow","green","blue","purple","darkslategray3","gray","black","pink","darkred","cornsilk"),
        beside = TRUE)
text.legend=row.names(locationgender)
col2 <- c("darkblue","red","orange","yellow","green","blue","purple","darkslategray3","gray","black","pink","darkred","cornsilk")
legend("topright",pch=c(15),legend=text.legend,col=col2,bty="n",ncol = 1,inset=c(-0.25,0))

```
##  Barplot of probabilities
```{r}
genderlocation_prop <- prop.table(genderlocation,2)
barplot(genderlocation_prop,main = "Gender and num of locations", 
        xlab = "Locations", ylab = "Probabilities",
        col=c("darkblue","red","orange","yellow","green","blue","purple","darkslategray3","gray","black","pink","darkred","cornsilk"))
text.legend=row.names(genderlocation_prop)
col2 <- c("darkblue","red","orange","yellow","green","blue","purple","darkslategray3","gray","black","pink","darkred","cornsilk")
legend("topright",pch=c(15),legend=text.legend,col=col2,bty="n",ncol = 1,inset=c(-0.25,0))

locationgender_prop <- prop.table(locationgender,2)
barplot(locationgender_prop,main = "Gender and num of locations", 
        xlab = "Locations",ylab = "Probabilities",
        col=c("darkblue","red","orange","yellow","green","blue","purple","darkslategray3","gray","black","pink","darkred","cornsilk"))
text.legend=row.names(locationgender_prop)
col2 <- c("darkblue","red","orange","yellow","green","blue","purple","darkslategray3","gray","black","pink","darkred","cornsilk")
legend("topright",pch=c(15),legend=text.legend,col=col2,bty="n",ncol = 1,inset=c(-0.25,0))
```
# Relationship between gender and number of location types
```{r}
num_of_locationTypes$gender <- encounter_subset$Gender
num_of_locationTypes$gender <- factor(num_of_locationTypes$gender,
                                  levels = c(1,2),
                                  labels = c("Male","Female"))
gendertype <- table(num_of_locationTypes$gender,num_of_locationTypes$X1L)
typegender <- table(num_of_locationTypes$X1L,num_of_locationTypes$gender)
barplot(gendertype,main = "Gender and num of location Types", 
        xlab = "Location Types",ylab = "Frequency",
        col = c("darkblue","red"),
        beside = TRUE)
text.legend=row.names(gendertype)
col2 <- c("darkblue","red")
legend("topright",pch=c(15),legend=text.legend,col=col2,bty="n",ncol = 1,inset=c(-0.25,0))

barplot(typegender,main = "Gender and num of location Types", 
        xlab = "Location Types",ylab = "Frequency",
        col=c("darkblue","red","orange","yellow","green","blue","purple","darkslategray3","gray"),
        beside = TRUE)
text.legend=row.names(typegender)
col2 <- c("darkblue","red","orange","yellow","green","blue","purple","darkslategray3","gray")
legend("topright",pch=c(15),legend=text.legend,col=col2,bty="n",ncol = 1,inset=c(-0.25,0))

```
##  Probabilities
```{r}
gendertype_prop <- prop.table(gendertype,2)
barplot(gendertype_prop,main = "Gender and num of location Types", 
        xlab = "Location Types",ylab = "Probabilities",
        col=c("darkblue","red","orange","yellow","green","blue","purple","darkslategray3","gray","black","pink","darkred","cornsilk"))
text.legend=row.names(gendertype_prop)
col2 <- c("darkblue","red","orange","yellow","green","blue","purple","darkslategray3","gray","black","pink","darkred","cornsilk")
legend("topright",pch=c(15),legend=text.legend,col=col2,bty="n",ncol = 1,inset=c(-0.25,0))

typegender_prop <- prop.table(typegender,2)
barplot(typegender_prop,main = "Gender and num of location Types", 
        xlab = "locationTypes",ylab = "Probabilities",
        col=c("darkblue","red","orange","yellow","green","blue","purple","darkslategray3","gray","black","pink","darkred","cornsilk"),
        legend = row.names(typegender_prop))
text.legend=row.names(typegender_prop)
col2 <- c("darkblue","red","orange","yellow","green","blue","purple","darkslategray3","gray","black","pink","darkred","cornsilk")
legend("topright",pch=c(15),legend=text.legend,col=col2,bty="n",ncol = 1,inset=c(-0.25,0))

```
# Unique locations
# Strip out movement data
```{r}
drop_transportation <- encounter[which(encounter$Location_Type != "Private Transport (private or rented car, motorbike)"),]
drop_transportation_pri <- drop_transportation[which(drop_transportation$Location_Type != "Public Transport (train, tram, bus or taxi)"),]
drop_transportation_all <- drop_transportation_pri[which(drop_transportation_pri$Location_Type != "Car journey (respondent alone in the car)"),]
```
##  Judge unique bases on (lantitude,lontitude)
```{r}
index <- duplicated(drop_transportation_all[,c(1,9,10)])
encounter_drop_transportation <- drop_transportation_all[!index,]

unique_location <- data.frame(num = numeric(0))
for(subject in encounter_subset$Subject){
  unique_location <- rbind(unique_location, nrow(encounter_drop_transportation[which(encounter_drop_transportation$Subject == subject), ]))
}
unique_location$subject <- encounter_subset$Subject
unique_location$age <- encounter_subset$Age
unique_location$gender <- encounter_subset$Gender
unique_location$age_range <- age_range_rep
```
## Boxplot and histogram
```{r}
boxplot(unique_location$X1L,main="boxplot for unique locations one has gone",ylab = "Num of locations")
hist(unique_location$X1L,main="histogram for unique locations one has gone",xlab = "Num of locations")
```
# Relationship between age and unique location
```{r}
boxplot(unique_location$X1L~unique_location$age_range,ylab = "Num of unique locations")
plot(unique_location$X1L~unique_location$age,xlab = "Age", ylab = "Num of unique locations")
```
##  Barplot of age range and unique location
```{r}
ageunique <- table(unique_location$X1L,unique_location$age_range)
uniqueage <- table(unique_location$age_range,unique_location$X1L)
barplot(ageunique, main="Age range and location types",
        xlab="Age range", ylab = "Frequency",
        col=c("darkblue","red","orange","yellow","green","blue","purple","darkslategray3","gray","black","pink","darkred","cornsilk"),
        beside=TRUE)
text.legend=row.names(ageunique)
col2 <- c("darkblue","red","orange","yellow","green","blue","purple","darkslategray3","gray","black","pink","darkred","cornsilk")
legend("topright",pch=c(15),legend=text.legend,col=col2,bty="n",ncol = 1,inset=c(-0.25,0))

barplot(ageunique, main="age range and location types",
        xlab="Age range", ylab = "Frequency",
        col=c("darkblue","red","orange","yellow","green","blue","purple","darkslategray3","gray","black","pink","darkred","cornsilk"))
text.legend=row.names(ageunique)
col2 <- c("darkblue","red","orange","yellow","green","blue","purple","darkslategray3","gray","black","pink","darkred","cornsilk")
legend("topright",pch=c(15),legend=text.legend,col=col2,bty="n",ncol = 1,inset=c(-0.25,0))

barplot(uniqueage, main="age range and location types",
        xlab="Unique location", ylab = "Frequency",
        col=c("darkblue","red","orange","yellow","green","blue","purple","darkslategray3","gray"),
        beside=TRUE)
text.legend=row.names(uniqueage)
col2 <- c("darkblue","red","orange","yellow","green","blue","purple","darkslategray3","gray")
legend("topright",pch=c(15),legend=text.legend,col=col2,bty="n",ncol = 1,inset=c(-0.25,0))

barplot(uniqueage, main="age range and location types",
        xlab="Unique location", ylab = "Frequency",
        col=c("darkblue","red","orange","yellow","green","blue","purple","darkslategray3","gray"))
text.legend=row.names(uniqueage)
col2 <- c("darkblue","red","orange","yellow","green","blue","purple","darkslategray3","gray")
legend("topright",pch=c(15),legend=text.legend,col=col2,bty="n",ncol = 1,inset=c(-0.25,0))

```
##  Probabilities
```{r}
ageunique_prop1 <- prop.table(ageunique,2)
barplot(ageunique_prop1, main="Probabilities age range and unique location",
        xlab="Age range", ylab = "Probabilities",
        col=c("darkblue","red","orange","yellow","green","blue","purple","darkslategray3","gray","black","pink","darkred","cornsilk"))
text.legend=row.names(ageunique_prop1)
col2 <- c("darkblue","red","orange","yellow","green","blue","purple","darkslategray3","gray","black","pink","darkred","cornsilk")
legend("topright",pch=c(15),legend=text.legend,col=col2,bty="n",ncol = 1,inset=c(-0.25,0))

uniqueage_prop <- prop.table(uniqueage,2)
barplot(uniqueage_prop, main="Probabilities age range and unique location",
        xlab="Unique locations", ylab = "Probabilities",
        col=c("darkblue","red","orange","yellow","green","blue","purple","darkslategray3","gray","black","pink","darkred","cornsilk"))
text.legend=row.names(uniqueage_prop)
col2 <- c("darkblue","red","orange","yellow","green","blue","purple","darkslategray3","gray","black","pink","darkred","cornsilk")
legend("topright",pch=c(15),legend=text.legend,col=col2,bty="n",ncol = 1,inset=c(-0.25,0))

```
# Relationship: gender and num of unique location
```{r}
boxplot(unique_location$X1L~unique_location$gender)
```
##  Barplot
```{r}
unique_location$gender <- factor(unique_location$gender,
                                      levels = c(1,2),
                                      labels = c("Male","Female"))
genderunique <- table(unique_location$gender,unique_location$X1L)
uniquegender <- table(unique_location$X1L,unique_location$gender)
barplot(genderunique,main = "Gender and num of unique location Types", 
        xlab = "Location types",ylab = "Frequency",
        col = c("darkblue","red"),
        beside = TRUE)
text.legend=row.names(genderunique)
col2 <- c("darkblue","red")
legend("topright",pch=c(15),legend=text.legend,col=col2,bty="n",ncol = 1,inset=c(-0.25,0))

barplot(uniquegender,main = "Gender and num of unique location", 
        xlab = "Location types",ylab = "Frequency",
        col=c("darkblue","red","orange","yellow","green","blue","purple","darkslategray3","gray","black","pink","darkred","cornsilk"),
        beside = TRUE)
text.legend=row.names(uniquegender)
col2 <- c("darkblue","red","orange","yellow","green","blue","purple","darkslategray3","gray","black","pink","darkred","cornsilk")
legend("topright",pch=c(15),legend=text.legend,col=col2,bty="n",ncol = 1,inset=c(-0.25,0))
```
##  Probabilities
```{r}
genderunique_prop <- prop.table(genderunique,2)
barplot(genderunique_prop,main = "Gender and num of unique location", 
        xlab = "Location", ylab = "Probabilities",
        col=c("darkblue","red","orange","yellow","green","blue","purple","darkslategray3","gray","black","pink","darkred","cornsilk"))
text.legend=row.names(genderunique_prop)
col2 <- c("darkblue","red","orange","yellow","green","blue","purple","darkslategray3","gray","black","pink","darkred","cornsilk")
legend("topright",pch=c(15),legend=text.legend,col=col2,bty="n",ncol = 1,inset=c(-0.25,0))

uniquegender_prop <- prop.table(uniquegender,2)
barplot(uniquegender_prop,main = "Gender and num of unique location", 
        xlab = "Location", ylab = "Probabilities",
        col=c("darkblue","red","orange","yellow","green","blue","purple","darkslategray3","gray","black","pink","darkred","cornsilk"))
text.legend=row.names(uniquegender_prop)
col2 <- c("darkblue","red","orange","yellow","green","blue","purple","darkslategray3","gray","black","pink","darkred","cornsilk")
legend("topright",pch=c(15),legend=text.legend,col=col2,bty="n",ncol = 1,inset=c(-0.25,0))

```
# The relationship between duration and different location types
```{r}
encounter_duration <- encounter[which(encounter$Duration!="NULL"), ]
encounter_type_duration <- encounter[which(encounter$Location_Type != "NULL"),]

encounter_type_duration$Location_Type <- factor(encounter_type_duration$Location_Type,
                                  levels = c("Home","Private Transport (private or rented car, motorbike)",
                                             "Retail and hospitality (bars, cafes, shops, hair dressing, etc.) ",
                                             "Car journey (respondent alone in the car)",
                                             "Sport and recreation","Other ","Work",
                                             "Public spaces (parks, streets, stations, airports etc.)",
                                             "Study (Uni, school, kindergarden, childcare centre etc)",
                                             "Arts and culture (cinema, library, gigs, museum, theatre etc.) ",
                                             "Public Transport (train, tram, bus or taxi)"),
                                  labels = c("H","PriT",
                                             "RT",
                                             "CJ",
                                             "SR","Other","Work",
                                             "PS",
                                             "Study",
                                             "AC",
                                             "PubT"))
Location_Type <- data.frame(sapply(encounter_type_duration$Location_Type, function(x) { if(is.factor(x)) {
  as.character(x)
} else {
  x
}
}))

Duration <- data.frame(sapply(encounter_type_duration$Duration, function(x) { if(is.factor(x)) {
  as.numeric(as.character(x))
} else {
  x
}
}))
encounter_type_duration$Location_Type <- Location_Type$sapply.encounter_type_duration.Location_Type..function.x...
encounter_type_duration$Duration <- Duration$sapply.encounter_type_duration.Duration..function.x...
boxplot(encounter_type_duration$Duration ~ encounter_type_duration$Location_Type, xlab = "location types",ylab = "Duration of staying at on different location type(mins)")
```

```{r}
encounter_type_duration$Duration[which(encounter_type_duration$Duration >= 0 & encounter_type_duration$Duration < 60)] <- 1
encounter_type_duration$Duration[which(encounter_type_duration$Duration >= 60 & encounter_type_duration$Duration < 120)] <- 2
encounter_type_duration$Duration[which(encounter_type_duration$Duration >= 120 & encounter_type_duration$Duration < 180)] <- 3
encounter_type_duration$Duration[which(encounter_type_duration$Duration >= 180 & encounter_type_duration$Duration < 240)] <- 4
encounter_type_duration$Duration[which(encounter_type_duration$Duration >= 240 & encounter_type_duration$Duration < 300)] <- 5
encounter_type_duration$Duration[which(encounter_type_duration$Duration >= 300 & encounter_type_duration$Duration < 360)] <- 6
encounter_type_duration$Duration[which(encounter_type_duration$Duration >= 360 & encounter_type_duration$Duration < 420)] <- 7
encounter_type_duration$Duration[which(encounter_type_duration$Duration >= 420)] <- "more than 7"
```
##  Barplot 
```{r}
type_duration <- table(encounter_type_duration$Location_Type,encounter_type_duration$Duration)
duration_type <- table(encounter_type_duration$Duration,encounter_type_duration$Location_Type)
barplot(type_duration,main = "Location type and duration", 
        xlab = "Duration",ylab = "Frequency",
        col=c("darkblue","red","orange","yellow","green","blue","purple","darkslategray3","gray","black","pink"),
        beside = TRUE)
text.legend=row.names(type_duration)
col2 <- c("darkblue","red","orange","yellow","green","blue","purple","darkslategray3","gray","black","pink")
legend("topright",pch=c(15),legend=text.legend,col=col2,bty="n",ncol = 1,inset=c(-0.25,0))

barplot(type_duration,main = "Location type and duration", 
        xlab = "Duration",ylab = "Frequency",
        col=c("darkblue","red","orange","yellow","green","blue","purple","darkslategray3","gray","black","pink"))
text.legend=row.names(type_duration)
col2 <- c("darkblue","red","orange","yellow","green","blue","purple","darkslategray3","gray","black","pink")
legend("topright",pch=c(15),legend=text.legend,col=col2,bty="n",ncol = 1,inset=c(-0.25,0))

barplot(duration_type,main = "Location type and duration", 
        xlab = "Location type",ylab = "Frequency",
        col=c("darkblue","red","orange","yellow","green","blue","purple","darkslategray3"),
        beside = TRUE)
text.legend=row.names(duration_type)
col2 <- c("darkblue","red","orange","yellow","green","blue","purple","darkslategray3")
legend("topright",pch=c(15),legend=text.legend,col=col2,bty="n",ncol = 1,inset=c(-0.25,0))

barplot(duration_type,main = "Location type and duration", 
        xlab = "Location type",ylab = "Frequency",
        col=c("darkblue","red","orange","yellow","green","blue","purple","darkslategray3"),
        legend = row.names(duration_type))
text.legend=row.names(duration_type)
col2 <- c("darkblue","red","orange","yellow","green","blue","purple","darkslategray3")
legend("topright",pch=c(15),legend=text.legend,col=col2,bty="n",ncol = 1,inset=c(-0.25,0))
```
