---
output:
  word_document: default
  html_document: default
---
```{r}
encounter <- read.csv("/Users/liyi/Desktop/RP/day_in_the_life.csv")
```
# How many unique subjects in this data set
```{r}
index <- duplicated(encounter[,1])
encounter_subset <- encounter[!index,]
(nrow(encounter_subset))
```
#How many males / females are in the data set?
# # The number of male in this dataset
```{r}
(nrow(encounter_subset[encounter_subset$Gender == 1,]))
```
# # The number of female in this dataset
```{r}
(nrow(encounter_subset[encounter_subset$Gender == 2,]))
```
# Age distribution for all of the subjects
# # mean and sd of age
```{r}
meanage = mean(encounter_subset$Age,rm.na = TRUE)
sdage = sd(encounter_subset$Age)
```
## plots of raw data of age
```{r}
stripchart(encounter_subset$Age, xlab = "age")
boxplot(encounter_subset$Age,horizontal = TRUE,xlab = "age")
```
## histgram
```{r}
hist(encounter_subset$Age,xlab = "age",ylab = "freq",main = "age distribution")
hist(encounter_subset$Age,xlab = "age",ylab = "freq",main = "age distribution",freq = FALSE)
curve(dnorm(x, 
            mean=meanage, 
            sd=sdage), 
      add=TRUE, 
      col="darkblue", 
      lwd=2)
```
## Plot distribution
```{r}
age_distribution <- dnorm(encounter_subset$Age, mean(encounter_subset$Age), sd = sd(encounter_subset$Age))
plot(encounter_subset$Age,age_distribution, xlab = "age")
```
## The summary of age distribution
```{r}
summary(encounter_subset$Age)
```
# Age distribution bases on gender
```{r}
par(mfrow=c(1,1))
boxplot(Age~Gender,data = encounter_subset,xlab = "gender",ylab = "age",main = "age~gender")
plot(Age~Gender,data = encounter_subset,xlab = "gender",ylab = "age")
hist(encounter_subset$Age[which(encounter_subset$Gender==1)],xlab = "age", main = "Age distribution of male")
hist(encounter_subset$Age[which(encounter_subset$Gender==1)],freq = FALSE, xlab = "age", main = "Age distribution of male")
curve(dnorm(x,
            mean = mean(encounter_subset$Age[which(encounter_subset$Gender==1)]),
            sd = sd(encounter_subset$Age[which(encounter_subset$Gender==1)])),
      add = TRUE)

hist(encounter_subset$Age[which(encounter_subset$Gender==2)],xlab = "age", main = "Age distribution of female")
hist(encounter_subset$Age[which(encounter_subset$Gender==2)],freq = FALSE, xlab = "age", main = "Age distribution of female")
curve(dnorm(x,
            mean = mean(encounter_subset$Age[which(encounter_subset$Gender==2)]),
            sd = sd(encounter_subset$Age[which(encounter_subset$Gender==2)])),
      add = TRUE)
```
## The summary of age based on gender
```{r}
summary(encounter_subset$Age[which(encounter_subset$Gender==1)])
summary(encounter_subset$Age[which(encounter_subset$Gender==2)])
```
# The distribution of the number of locations visited by each study participant
```{r}
num_of_locations <- data.frame(num = numeric(0))
for(subject in encounter_subset$Subject){
  #print(subject)
  num_of_locations <- rbind(num_of_locations, nrow(encounter[which(encounter$Subject == subject), ]))
  #nrow(encounter[which(encounter$Subject == subject), ])
}
nrow(num_of_locations)
hist(num_of_locations$X1L,xlab = "number of locations",main = "distribution of number of locations")
hist(num_of_locations$X1L,freq = FALSE,xlab = "number of locations",main = "distribution of number of locations")
curve(dnorm(x,
            mean = mean(num_of_locations$X1L),
            sd = sd(num_of_locations$X1L)),
      add = TRUE)

boxplot(num_of_locations$X1L,horizontal = TRUE)
stripchart(num_of_locations$X1L)
num_of_locations_distribution <- dnorm(num_of_locations$X1L, mean=mean(num_of_locations$X1L), sd = sd(num_of_locations$X1L))
plot(num_of_locations$X1L,num_of_locations_distribution,xlab = "number of locations",main = "distribution of number of locations")
```
#What is the distribution of number of different *types* of locations visited by each study participant?
```{r}
index <- duplicated(encounter[,c(1,6)])
encounter_subset_locationType <- encounter[!index,]
encounter_subset_locationType[c(1,2,3,4,5),]
num_of_locationTypes <- data.frame(num = numeric(0))
for(subject in encounter_subset$Subject){
  num_of_locationTypes <- rbind(num_of_locationTypes, nrow(encounter_subset_locationType[which(encounter_subset_locationType$Subject == subject), ]))
}
hist(num_of_locationTypes$X1L,xlab = "number of location types",main = "distribution of number of location types")
hist(num_of_locationTypes$X1L,freq = FALSE,xlab = "number of location types",main = "distribution of number of location types")
curve(dnorm(x,
            mean = mean(num_of_locationTypes$X1L),
            sd = sd(num_of_locationTypes$X1L)),
      add = TRUE)

boxplot(num_of_locationTypes$X1L,horizontal = TRUE)
stripchart(num_of_locationTypes$X1L)
num_of_locationTypes_distribution <- dnorm(num_of_locationTypes$X1L, mean=mean(num_of_locationTypes$X1L), sd = sd(num_of_locationTypes$X1L))
plot(num_of_locationTypes$X1L,num_of_locationTypes_distribution)
```
# What is the distribution of times spent at locations?
```{r}
encounter_duration <- read.csv("/Users/liyi/Desktop/RP/day_in_the_life.csv")
encounter_with_duration_subset <- encounter_duration[which(encounter_duration$Duration!="NULL"), ]
hist(as.numeric(as.character(encounter_with_duration_subset$Duration)),xlab = "duration",main = "distribution of duration")
hist(as.numeric(as.character(encounter_with_duration_subset$Duration)),freq = FALSE,xlab = "duration",main = "distribution of duration")
meanvalue <- mean(as.numeric(as.character(encounter_with_duration_subset$Duration)),na.rm=TRUE)
sdvalue <- sd(as.numeric(as.character(encounter_with_duration_subset$Duration)),na.rm=TRUE)
curve(dnorm(x,
            mean = meanvalue,
            sd = sdvalue),
      add = TRUE)

# encounter_with_duration_subset_single <- na.omit(encounter_with_duration_subset$Duration)
duration_location_distribution <- dnorm(na.omit(as.numeric(as.character(encounter_with_duration_subset$Duration))), mean = meanvalue, sd = sdvalue)
plot(na.omit(as.numeric(as.character(encounter_with_duration_subset$Duration))),duration_location_distribution,xlab = "duration",ylab = "distribution",main = "distribution of duration")
```



















